Template Master's Thesis

### 2023-08-15 paper.tex
Add tornado cash heuristics results

We found only 2 Tornado cash withdrawal transactions within our dataset.

>>>>

We identified 84 transactions tied to Tornado cash pools, including 72 deposits, 10 withdrawals, and two transactions where the same address sent 0.1 Ether to the corresponding pool without invoking the deposit function.  Despite applying all clustering heuristics except "Torn minting," we found no clusters.
